A* with Perfect Potentials

### 2020-06-10 paper/ch_potentials.tex
foo

TODO: Cite Sabine VLDB and TopoCore

@@

>>>>

Simple Routes: https://dl.acm.org/doi/10.1145/2525314.2525362 example of flexibility need

EV: https://dl.acm.org/doi/10.1145/2666310.2666382
EV: https://dl.acm.org/doi/10.1145/2820783.2820826

Traffic Planning: https://dl.acm.org/doi/10.1145/2666310.2666406 uses an A* search with adjusted costs

Learning Cost functions with CRP: https://dl.acm.org/doi/10.1145/2820783.2820808 strong argument for flexibility. Must Cite.
Also Learning Cost functions: https://dl.acm.org/doi/10.1145/2996913.2997004 Must Cite.

Personalized Route Planning: https://dl.acm.org/doi/10.1145/2820783.2820830 exact same motivation argument as our paper. Must Cite. 
TopoCore: https://dl.acm.org/doi/10.1145/2820783.2820856 Must Cite.

Compute Travel Time Probability Per arc: https://dl.acm.org/doi/10.1145/2820783.2820836 Bullshit contentwise. However, could be cited in TD context.

Travel Time Probability with A*: https://dl.acm.org/doi/10.1145/2996913.2996964

Historic Travel Time Function Computation : https://dl.acm.org/doi/10.1145/2996913.2996988 not really relevant but could be cited.

Most preferred path: https://dl.acm.org/doi/10.1145/3139958.3140029

Off-Topic Important for Map-Matching: https://dl.acm.org/doi/10.1145/2525314.2525466

@@

Historic travel time : $w_h(e,\tau)$

Live travel time : $w_c(e)$

Lower bound travel time : $w_\ell(e)$

$\tau_{\mathrm{now}}$ : the current moment in time

$\tau_{\mathrm{soon}}$ : now plus one hour

A* works on $w_q(e,\tau)$ which is defined as follows:

$w_q(e,\tau) = w_c(e)$ for $\tau \le \tau_{\mathrm{soon}}$

If $w_h(e,\tau_{\mathrm{soon}}) < w_c(e)$, then $w_q(e,\tau) = \max\{w_c(e)+(\tau_{\mathrm{soon}}-\tau), w_h(e,\tau)\}$ for $\tau \ge \tau_{\mathrm{soon}}$.

If $w_h(e,\tau_{\mathrm{soon}}) = w_c(e)$, then $w_q(e,\tau) = w_h(e,\tau)$ for $\tau \ge \tau_{\mathrm{soon}}$.

If $w_h(e,\tau_{\mathrm{soon}}) > w_c(e)$, then $w_q(e,\tau) = \min\{w_c(e)-(\tau_{\mathrm{soon}}-\tau), w_h(e,\tau)\}$ for $\tau \ge \tau_{\mathrm{soon}}$.
